---
title: "Controllo di qualità dei dati (DARIO) - Coorte 2023"
title-block-banner: true
date: today
format:
    pdf:
      toc: true
      toc-depth: 4
      number-sections: true
      highlight-style: github
      fontsize: "10"
      geometry:
        - top=20mm
        - bottom=20mm
        - left=20mm
        - right=20mm
        - heightrounded
editor: visual
---

\pagebreak

# Controllo di qualità dei dati (DARIO)

## Configuration

```{r}
#| warning: false
#| echo: false

#rm(list=ls())

cat("Starting configuration\n")

# packages

baseDir = getwd()
source(paste0(baseDir,"/config.R"), echo = TRUE)
source(paste0(baseDir,"/codice/rbiostatfunbox/funbox.R"), echo = TRUE)

library(readxl)
library(readr)
library(dplyr)
library(knitr)
library(janitor)
library(kableExtra)
library(scales)
library(ggplot2)
library(survminer)

# path

wd = baseDir
setwd(wd)
indir = exportDir
outdir <- paste0(exportDir, "/outdir")

# funtions

# ===============================
# FUNZIONE CONTEGGIO MISSING

count_missing_types <- function(x){
  
  x_chr <- as.character(x)
  
  tibble(
    `9`           = sum(x_chr == "9", na.rm = TRUE),
    `99`          = sum(x_chr == "99", na.rm = TRUE),
    `999`         = sum(x_chr == "999", na.rm = TRUE),
    `9999`        = sum(x_chr == "9999", na.rm = TRUE),
    `-`           = sum(x_chr == "-", na.rm = TRUE),
    `xxxx/xx/xx`  = sum(x_chr == "xxxx/xx/xx", na.rm = TRUE),
    `2222/22/22`  = sum(x_chr == "2222/22/22", na.rm = TRUE),
    `222222`  = sum(x_chr == "222222", na.rm = TRUE),
    `NA`          = sum(is.na(x))
  )
}

# ===============================
# COSTRUZIONE TABELLA MISSING

build_missing_table <- function(data){
  
  res <- lapply(names(data), function(v){
    
    out <- count_missing_types(data[[v]])
    out$Variabile <- v
    out
  })
  
  bind_rows(res) %>%
    select(Variabile, everything())
}

# ===============================
# SUMMARY NUMERICHE

summary_numeric <- function(data, var){
  
  x <- data[[var]]
  x_clean <- x[!(x %in% sentinel_num) & !is.na(x)]
  
  if(length(x_clean) == 0){
    return(
      tibble(
        Stat  = c("Media","Mediana","Moda","SD","IQR","Missing"),
        Value = c(NA, NA, NA, NA, NA, count_missing(x))
      )
    )
  }
  
  tibble(
    Stat = c("Media","Mediana","Moda","SD","IQR","Missing"),
    Value = c(
      round(mean(x_clean, na.rm = TRUE), 2),
      round(median(x_clean, na.rm = TRUE), 2),
      mode_stat(x_clean),
      round(sd(x_clean, na.rm = TRUE), 2),
      round(IQR(x_clean, na.rm = TRUE), 2),
      count_missing(x)
    )
  )
}

# ===============================
# SUMMARY CATEGORICHE

summary_categorical <- function(data, var){
  x <- data[[var]]
  
  tab <- table(x, useNA = "ifany")
  df  <- as.data.frame(tab)

}

# ===============================
# SENTINEL VALUES

sentinel_num <- c(9, 99, 999, 9999, 99999)
sentinel_fac <- c(
  "9","99","999","9999","99999",
  "0",""," ","NA","N/A","XXXX/XX/XX","-"
)

# ===============================
# count_missing

count_missing <- function(x){
  if(is.numeric(x)){
    sum(is.na(x) | x %in% sentinel_num)
  } else {
    sum(is.na(x) | as.character(x) %in% sentinel_fac)
  }
}


# ===============================
# mode_stat

mode_stat <- function(x){
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}

cat("DONE\n")
```

## Data

```{r}
#| warning: false
#| echo: false

cat("Loading data\n")

eurocatData_merged_last_pre_DMS <- read.csv2(
  paste0(exportDir, "/eurocatData.csv"),
  stringsAsFactors = FALSE
)

# FIX UTF-8 GLOBALE 
# eurocatData_merged_last_pre_DMS[] <- lapply(
#   eurocatData_merged_last_pre_DMS,
#   function(x){
#     if(is.character(x)){
#       x <- iconv(x, from = "", to = "UTF-8", sub = "")
#       x <- enc2utf8(x)
#     }
#     x
#   }
# )

# remove first column (solo se davvero necessario)
# eurocatData_merged_last_pre_DMS <- 
#   eurocatData_merged_last_pre_DMS[, -1]

cat("DONE\n")

cat(paste0("Number of record: ", 
           nrow(eurocatData_merged_last_pre_DMS), "\n"))

cat(paste0("Number of vars: ", 
           ncol(eurocatData_merged_last_pre_DMS), "\n"))

# sanitize character variable

cat("Cleaning\n")

spCols <- grep("^sp_", colnames(eurocatData_merged_last_pre_DMS))
spCols <- c(spCols, 18, 34, 112)

for(spcol in spCols){
  eurocatData_merged_last_pre_DMS[[spcol]] <- 
    iconv(eurocatData_merged_last_pre_DMS[[spcol]],
          from = "", to = "UTF-8", sub = "")
  
  eurocatData_merged_last_pre_DMS[[spcol]] <- 
    gsub("[^[:alnum:][:space:]]", "", 
         eurocatData_merged_last_pre_DMS[[spcol]])
}

eurocatData_merged_last_pre_DMS$cod_pres <- as.factor(str_replace_all(eurocatData_merged_last_pre_DMS$cod_pres, "\\|", ";"))

eurocatData_merged_last_pre_DMS$pm_notes <- iconv(eurocatData_merged_last_pre_DMS$pm_notes, from = "", to = "UTF-8", sub = "")

cat("DONE\n")

# variable set for tabulation

cat("Variables selection\n")

noTab <- c("record_id", "birth_date", "centre", "numloc", "sdo_number", "datemo", "prog_paz_neo", "cedap_linked", "sp_twin", "death_date", "mocitizenship", "resmo", "extra_er_resmo", "sp_karyo", "sp_gentest", "pm_notes", "syndrome", "sp_syndrome", "malfo1", "sp_malfo1", "malfo2", "sp_malfo2", "malfo3", "sp_malfo3", "malfo4", "sp_malfo4", "malfo5", "sp_malfo5", "malfo6", "sp_malfo6", "malfo7", "sp_malfo7", "malfo8", "sp_malfo8", "illbef1", "sp_illbef1", "illbef2", "sp_illbef2", "illdur1", "sp_illdur1", "illdur2", "sp_illdur2", "drugs1", "sp_drugs", "drugs2", "sp_drugs_2", "drugs3", "sp_drugs_3", "drugs4", "sp_drugs_4", "drugs5", "sp_drugs_5", "genrem", "omim", "orpha", "agefa", "occupmo", "sp_sibanom", "sp_moanom", "sp_faanom")

toTab <- setdiff(colnames(eurocatData_merged_last_pre_DMS), noTab)

tabSet<-eurocatData_merged_last_pre_DMS |> select(toTab)

cat("DONE\n")

```

## Analysis

### Linkage

```{r}
#| label: Linkage
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS %>%
  mutate(
    cedap_linked_binary = ifelse(cedap_linked == 0, "No", "Yes")
  ) %>%
  count(cedap_linked_binary, name = "n") %>%
  filter(n > 1) %>%
  knitr::kable(col.names = c("Linked to CedAP", "n")) %>%
  row_spec(row = 0, background = 'lightgray') %>%
  column_spec(1, width = "10cm") %>%
  kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\n\\newpage\n")
```

### Missings table

```{r}
#| echo: false
#| warning: false
#| results: asis

nm<-nmiss(eurocatData_merged_last_pre_DMS)[,3:6]
nm$percentMissing <- round(nm$percentMissing, 2)
knitr::kable(nm)
cat("\n\n\\newpage\n")

write.csv2(
  nm,
  file = file.path(outdir, "missings.csv")
)

```

### Missings table with EUROCAT codes

```{r}
#| echo: false
#| warning: false
#| results: asis

missing_eurocat <- build_missing_table(eurocatData_merged_last_pre_DMS)
knitr::kable(missing_eurocat)
cat("\n\n\\newpage\n")

write.csv2(
  missing_eurocat,
  file = file.path(outdir, "missings_EUROCAT.csv")
)

```

### Type of the variables

```{r}
#| echo: false
#| warning: false
#| fig-align: center
#| results: asis

vis_dat_wrapper(eurocatData_merged_last_pre_DMS)
cat("\n\n\\newpage\n")
```

### Description of the variables

```{r}
#| label: Set variables type
#| echo: false
#| warning: false


numeric_vars <- c(
  "weight","gestlength","agemo","bmi","agedisc"
)
factor_vars <- setdiff(names(eurocatData_merged_last_pre_DMS), numeric_vars)

eurocatData_merged_last_pre_DMS[factor_vars] <- lapply(eurocatData_merged_last_pre_DMS[factor_vars], as.factor)

eurocatData_merged_last_pre_DMS[numeric_vars] <- lapply(eurocatData_merged_last_pre_DMS[numeric_vars], as.numeric)
```

#### record_id

Table below reports only record_id with frequency greater than 1.

```{r}
#| label: Record ID
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS %>%
  count(record_id, name = "n") %>%
  filter(n > 1) %>%
  knitr::kable() %>%
  row_spec(row = 0, background = 'lightgray') %>%
  column_spec(1, width = "10cm") %>%
  kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\n\\newpage\n")
```

#### birth_date

```{r}
#| label: Birth date
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(birth_date)) + geom_bar() + xlab("birth_date") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$birth_date, eurocatData_merged_last_pre_DMS$cod_pres, useNA = "ifany"))
colnames(tab)[1:2] <- c("birth_date", "cod_pres")

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "5cm") %>% column_spec(2, width = "5cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### numloc

Table below reports only numloc with frequency greater than 1.

```{r}
#| label: numloc
#| echo: false
#| warning: false
#| results: asis

tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$numloc, useNA = "ifany"))
colnames(tab)[1] <- "numloc"

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped", linesep = ""), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### sdo_number

Table below reports only sdo_number with frequency greater than 1.

```{r}
#| label: sdo_number
#| echo: false
#| warning: false
#| results: asis

tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sdo_number, useNA = "ifany"))
colnames(tab)[1] <- "sdo_number"

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### datemo

```{r}
#| label: datemo
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2


brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(datemo)) + geom_bar() + xlab("datemo") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$datemo, eurocatData_merged_last_pre_DMS$cod_pres, useNA = "ifany"))
colnames(tab)[1:2] <- c("datemo", "cod_pres")

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "5cm") %>% column_spec(2, width = "5cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### prog_paz_neo

Table below reports only prog_paz_neo with frequency greater than 1.

```{r}
#| label: prog_paz_neo
#| echo: false
#| warning: false
#| results: asis

tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$prog_paz_neo, useNA = "ifany"))
colnames(tab)[1] <- "prog_paz_neo"

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### death_date

```{r}
#| label: death_date
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(death_date)) + geom_bar() + xlab("death_date") + ylab("counts(%)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$death_date, useNA = "ifany"))
colnames(tab)[1] <- c("death_date")

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### mocitizenship

```{r}
#| label: mocitizenship
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$mocitizenship, useNA = "ifany"))
colnames(tab)[1] <- "mocitizenship"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### resmo

```{r}
#| label: resmo
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$resmo, useNA = "ifany"))
colnames(tab)[1] <- c("resmo")

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### extra_er_resmo

```{r}
#| label: extra_er_resmo
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$extra_er_resmo, useNA = "ifany"))
colnames(tab)[1] <- c("extra_er_resmo")

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### cod_pres

```{r}
#| label: cod_pres
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(cod_pres)) + geom_bar() + xlab("cod_pres") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$cod_pres, useNA = "ifany"))
colnames(tab)[1] <- c("cod_pres")

tab %>%
  knitr::kable(escape = F) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### syndrome

```{r}
#| label: syndrome
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$syndrome, useNA = "ifany"))
          if(nrow(tab)>0){
          brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(syndrome)) + geom_bar(aes(y = (..count..)/sum(..count..))) +  scale_y_continuous(labels=scales::percent) +  scale_x_discrete(labels = label_wrap(10)) + xlab("syndrome") + ylab("counts(%)") + theme_light() + theme(axis.text = element_blank())
          print(brp)
          cat("\n")
          colnames(tab)[1] <- "syndrome"
          print(
            tab %>%
            knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
          )
          }
cat("\n\n\\newpage\n")
```

#### sp_syndrome

```{r}
#| label: sp_syndrome
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_syndrome, useNA = "ifany"))
colnames(tab)[1] <- "sp_syndrome"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### malfo

```{r}
#| label: malfo
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

malfoSet <- eurocatData_merged_last_pre_DMS %>% select(c("malfo1", "malfo2", "malfo3", "malfo4", "malfo5", "malfo6", "malfo7", "malfo8"))

for(var in colnames(malfoSet)){
   
  tab <- as.data.frame(table(malfoSet[[var]], useNA = "ifany"))
          if(nrow(tab)>0){
            cat("#####", var, "\n")
            {
              brp <- malfoSet %>% ggplot(aes(get(var))) + geom_bar(aes(y = (..count..)/sum(..count..))) + scale_y_continuous(labels=scales::percent) +  xlab(var) + ylab("counts(%)") + theme_light() + theme(axis.text.x=element_blank())
          print(brp)
          cat("\n")
          }
          colnames(tab)[1] <- var
          print(
            tab %>%
            knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
          )
          }
  cat("\n\\newpage\n")
      }
```

#### sp_malfo

```{r}
#| label: sp_malfo
#| echo: false
#| warning: false
#| results: asis


malfoSet <- eurocatData_merged_last_pre_DMS %>% select(c("sp_malfo1", "sp_malfo2", "sp_malfo3", "sp_malfo4", "sp_malfo5", "sp_malfo6", "sp_malfo7", "sp_malfo8"))

for(var in colnames(malfoSet)){
  tab <- as.data.frame(table(malfoSet[[var]])) 
  if(nrow(tab)>0){
    cat("#####", var, "\n")
    colnames(tab)[1] <- var
          print(
            tab %>%
            knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
          )
  cat("\n\\newpage\n")
  }
}
    
```

```{r}
#| label: other_variables
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

for(var in colnames(eurocatData_merged_last_pre_DMS[, toTab])){

  cat("####", var, "\n")
   
   if(is.numeric(eurocatData_merged_last_pre_DMS[[var]])){
     bxp<-ggplot(eurocatData_merged_last_pre_DMS, aes(y=get(var))) + geom_boxplot() + scale_x_discrete(labels = label_wrap(5)) + ylab(var) + theme_light()
     print(bxp)
     cat("\n")
     tab <- summary_numeric(eurocatData_merged_last_pre_DMS, var)
      if(nrow(tab)>0){
        colnames(tab)[1] <- var
        print(
          tab %>%
          knitr::kable(position = "left", full_width = T)  %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
        )
     }
    } else {
          tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS[[var]], useNA = "ifany"))
          if(nrow(tab)>0){
          brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(get(var))) + geom_bar(aes(y = (..count..)/sum(..count..))) +  scale_y_continuous(labels=scales::percent) +  scale_x_discrete(labels = label_wrap(10)) + xlab(var) + ylab("counts(%)") + theme_light()
          print(brp)
          cat("\n")
          colnames(tab)[1] <- var
          print(
            tab %>%
            knitr::kable(position = "left", full_width = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
          )
          }
      }
    
    cat("\n\\newpage\n")
}
```

#### sp_twin

```{r}
#| label: sp_twin
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_twin, useNA = "ifany"))
colnames(tab)[1] <- "sp_twin"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### sp_karyo

```{r}
#| label: sp_karyo
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_karyo, useNA = "ifany"))
colnames(tab)[1] <- "sp_karyo"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### sp_gentest

```{r}
#| label: sp_gentest
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_gentest, useNA = "ifany"))
colnames(tab)[1] <- "sp_gentest"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### pm_notes

```{r}
#| label: pm_notes
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$pm_notes, useNA = "ifany"))
colnames(tab)[1] <- "pm_notes"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### drugs

```{r}
#| label: drug
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

malfoSet <- eurocatData_merged_last_pre_DMS %>% select(c("drugs1", "drugs2", "drugs3", "drugs4", "drugs5"))

for(var in colnames(malfoSet)){
   
  tab <- as.data.frame(table(malfoSet[[var]], useNA = "ifany"))
          if(nrow(tab)>0){
            cat("#####", var, "\n")
            {
              brp <- malfoSet %>% ggplot(aes(get(var))) + geom_bar(aes(y = (..count..)/sum(..count..))) + scale_y_continuous(labels=scales::percent) +  xlab(var) + ylab("counts(%)") + theme_light() + theme(axis.text.x=element_blank())
          print(brp)
          cat("\n")
          }
          colnames(tab)[1] <- var
          print(
            tab %>%
            knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
          )
          }
  cat("\n\\newpage\n")
      }
```

#### sp_drugs

```{r}
#| label: sp_drug
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

malfoSet <- eurocatData_merged_last_pre_DMS %>% select(c("sp_drugs", "sp_drugs_2", "sp_drugs_3", "sp_drugs_4", "sp_drugs_5"))

for(var in colnames(malfoSet)){
   
  tab <- as.data.frame(table(malfoSet[[var]], useNA = "ifany"))
          if(nrow(tab)>0){
            cat("#####", var, "\n")
              colnames(tab)[1] <- var
              print(
              tab %>%
              knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
            )
            }
    cat("\n\\newpage\n")
        }

```

#### illbef1

```{r}
#| label: illbef1
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(illbef1)) + geom_bar() + xlab("illbef1") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$illbef1, useNA = "ifany"))
colnames(tab)[1] <- c("illbef1")

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "5cm") %>% column_spec(2, width = "5cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### sp_illbef1

```{r}
#| label: sp_illbef1
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_illbef1, useNA = "ifany"))
colnames(tab)[1] <- "sp_illbef1"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### illbef2

```{r}
#| label: illbef2
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(illbef2)) + geom_bar() + xlab("illbef2") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$illbef2, useNA = "ifany"))
colnames(tab)[1] <- c("illbef2")

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "5cm") %>% column_spec(2, width = "5cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### sp_illbef2

```{r}
#| label: sp_illbef2
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_illbef2, useNA = "ifany"))
colnames(tab)[1] <- "sp_illbef2"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### illdur1

```{r}
#| label: illdur1
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(illdur1)) + geom_bar() + xlab("illdur1") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$illdur1, useNA = "ifany"))
colnames(tab)[1] <- c("illdur1")

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "5cm") %>% column_spec(2, width = "5cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### sp_illdur1

```{r}
#| label: sp_illdur1
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_illdur1, useNA = "ifany"))
colnames(tab)[1] <- "sp_illdur1"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

#### illdur2

```{r}
#| label: illdur2
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

brp<-ggplot(eurocatData_merged_last_pre_DMS, aes(illdur2)) + geom_bar() + xlab("illdur2") + ylab("counts(n)") + theme_light() + theme(axis.text.x=element_blank())
print(brp)

tab<-as.data.frame(table(eurocatData_merged_last_pre_DMS$illdur2, useNA = "ifany"))
colnames(tab)[1] <- c("illdur2")

tab %>% filter(Freq>1) %>%
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "5cm") %>% column_spec(2, width = "5cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\n\\newpage\n")
```

#### sp_illdur2

```{r}
#| label: sp_illdur2
#| echo: false
#| warning: false
#| results: asis


tab <- as.data.frame(table(eurocatData_merged_last_pre_DMS$sp_illdur2, useNA = "ifany"))
colnames(tab)[1] <- "sp_twin"

tab %>% 
  knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()
cat("\n\\newpage\n")
```

```{r}
#| label: sp_other
#| echo: false
#| warning: false
#| results: asis
#| fig-align: "center"
#| fig-width: 3
#| fig-height: 2

malfoSet <- eurocatData_merged_last_pre_DMS %>% select(c("omim", "orpha", "agefa", "occupmo", "sp_sibanom", "sp_moanom", "sp_faanom"))

for(var in colnames(malfoSet)){
   
  tab <- as.data.frame(table(malfoSet[[var]], useNA = "ifany"))
          if(nrow(tab)>0){
            cat("#####", var, "\n")
              colnames(tab)[1] <- var
              print(
              tab %>%
              knitr::kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, width = "10cm") %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10)
            )
            }
    cat("\n\\newpage\n")
        }
```

## Cross tabulations

### Sex by type of birth

**Sex**: 1 = Male 2 = Female 3 = Indeterminate 9 = Not known

**Type of birth**: 1 = Live birth 2 = Stillbirth 3 = Spontaneous abortion 4 = TOPFA 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: sex_type
#| echo: false
#| warning: false
#| results: asis


sexTypeTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(sex, type) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

sexTypeTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### Sex unknown AND live birth by data_source

**Sex**: 1 = Male 2 = Female 3 = Indeterminate 9 = Not known

**Type of birth**: 1 = Live birth 2 = Stillbirth 3 = Spontaneous abortion 4 = TOPFA 9 = Not known

**data_sources**: 1 = EDC 2 = SDO

**Not admissible values**: to be defined

```{r}
#| label: Sex unknown AND live birth by data_source
#| echo: false
#| warning: false
#| results: asis


filtered_data <- eurocatData_merged_last_pre_DMS %>% 
  filter(sex == 9 & type == 1)

if (nrow(filtered_data) == 0) {

  cat("No records with sex == 9 and type == 1\n")

} else {

  sexTypeTable <- filtered_data %>% 
    tabyl(sex, data_source) %>% 
    adorn_totals(where = c("row", "col")) %>%
    adorn_percentages("row") %>%
    adorn_pct_formatting() %>%
    adorn_ns(position = "front") %>%
    adorn_title("combined")

  sexTypeTable %>%
    kable(fixed_thead = TRUE) %>% 
    row_spec(row = 0, background = 'lightgray') %>% 
    column_spec(1, bold = TRUE) %>% 
    kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
    print()
}

cat("\n\\newpage\n")
```

### Survival by type of birth

**Survival**: 1 = Yes 2 = No 3 = Alive at discharge \<1 week 9 = Not known

**Type of birth**: 1 = Live birth 2 = Stillbirth 3 = Spontaneous abortion 4 = TOPFA 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: surv_type
#| echo: false
#| warning: false
#| results: asis


survivalTypeTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(survival, type) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

survivalTypeTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### datemo (NA) by data_source

Missing mother birth date by data source.

```{r}
#| label: datemo_data_source
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$missing_datemo <- ifelse(is.na(eurocatData_merged_last_pre_DMS$datemo), "Yes", "No")
missDatemoDataSourceTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(missing_datemo, data_source) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

missDatemoDataSourceTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### Survival by death date

Casi, esclusi TOPFA, che sono registrati come non sopravvissuti alla prima settimana di vita ma per cui non è presente la data d morte.

**Survival**: 1 = Yes 2 = No 3 = Alive at discharge \<1 week 9 = Not known

```{r}
#| label: surv_death_date
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$surv_deathadate <- ifelse(is.na(eurocatData_merged_last_pre_DMS$death_date) | eurocatData_merged_last_pre_DMS$death_date == "222222", "Missing", "Available")

survDeathDateTable <- eurocatData_merged_last_pre_DMS %>% 
  filter(type != 4) %>%
  tabyl(survival, surv_deathadate) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

survDeathDateTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### nbrmalf by nbrbaby

**nbrmalf**: 1 = One 2 = Two 3 = Three 4 = Four 5 = Five 6 = Six or more 9 = Not known

**nbrbaby**: 1 = Singleton 2 = Twins 3 = Triplets 4 = Quadruplets 5 = Quintuplets 6 = Sextuplets or more 7 = Multiple birth, number of babies not known 8 = Singleton at time of delivery/termination, but known to have been a multiple pregnancy at an earlier stage in pregnancy 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: nbrmalf_nbrbaby
#| echo: false
#| warning: false
#| results: asis

nbrMalfBabyTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(nbrmalf, nbrbaby) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

nbrMalfBabyTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### firstpre by whendisc

**firstpre**: 1 = Ultrasound at GA \< 14 weeks 2 = Ultrasound at GA 14-21 weeks 3 = Ultrasound at GA ≥ 22 weeks 4 = Ultrasound GA not known 5 = Serum/ combined screening 6 = Chorion villus sampling or amniocentesis 7 = Other test positive 8 = Test(s) performed, result negative 9 = Not known 10 = No test performed 11 = Fetal karyotype on maternal blood

**whendisc**: 1 = At birth 2 = Less than 1 week 3 = 1-4 weeks 4 = 1-12 months 5 = Over 12 months 6 = Prenatal diagnosis in live fetus 7 = At abortion (spontaneous) 9 = Not known 10 = Postnatal diagnosis, age not known

**Not admissible values**: to be defined

```{r}
#| label: firstpre_whendisc
#| echo: false
#| warning: false
#| results: asis
#| 

firstpreWhendiscTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(firstpre, whendisc) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

firstpreWhendiscTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = "scale_down", font_size = 8) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### presyn by whendisc

**presyn**: 1 = Yes, this anomaly was diagnosed prenatally 2 = No, this anomaly was diagnosed postnatally 9 = Not known

**whendisc**: 1 = At birth 2 = Less than 1 week 3 = 1-4 weeks 4 = 1-12 months 5 = Over 12 months 6 = Prenatal diagnosis in live fetus 7 = At abortion (spontaneous) 9 = Not known 10 = Postnatal diagnosis, age not known

**Not admissible values**: to be defined

```{r}
#| label: presyn_whendisc
#| echo: false
#| warning: false
#| results: asis
#| 

presynWhendiscTable <- eurocatData_merged_last_pre_DMS %>% 
  filter(!is.na(syndrome)) %>%
  tabyl(presyn, whendisc) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

presynWhendiscTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = "scale_down", font_size = 8) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### gentest by karyo

**gentest**: 1 = specific genetic test positive 2 = specific genetic test negative 3 = Specific genetic test not Performed 9 = Not Known if genetic test is performed or result not known

**karyo**: 1 = Performed, result known 2 = Performed, results not known 3 = Not performed 4 = Probe test performed 8 = Failed 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: gentest_karyo
#| echo: false
#| warning: false
#| results: asis

gentestKaryoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(gentest, karyo) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

gentestKaryoTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### pm by type

**pm**: 1 = Performed, results known 2 = Performed, results not known 3 = Not performed 4 = Macerated fetus 9 = Not known

**Type of birth**: 1 = Live birth 2 = Stillbirth 3 = Spontaneous abortion 4 = TOPFA 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: pm_type
#| echo: false
#| warning: false
#| results: asis

pmTypeTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(pm, type) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

pmTypeTable %>%
  kable(fixed_thead = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo1 and sp_malfo1 (missing)

```{r}
#| label: malfo1_sp_malfo1
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo1 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo1 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo1), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo1, isnaSp_malfo1) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable(fixed_thead = T, longtable = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>% print()

cat("\n\\newpage\n")
```

### malfo2 and sp_malfo2 (missing)

```{r}
#| label: malfo2_sp_malfo2
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo2 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo2 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo2), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo2, isnaSp_malfo2) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable(fixed_thead = T, longtable = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo3 and sp_malfo3 (missing)

```{r}
#| label: malfo3_sp_malfo3
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo3 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo3 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo3), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo3, isnaSp_malfo3) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable(fixed_thead = T, longtable = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo4 and sp_malfo4 (missing)

```{r}
#| label: malfo4_sp_malfo4
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo4 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo4 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo4), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo4, isnaSp_malfo4) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable(fixed_thead = T, longtable = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo5 and sp_malfo5 (missing)

```{r}
#| label: malfo5_sp_malfo5
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo5 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo5 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo5), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo5, isnaSp_malfo5) %>% 
  #adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable(fixed_thead = T, longtable = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo6 and sp_malfo6 (missing)

```{r}
#| label: malfo6_sp_malfo6
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo6 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo6 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo6), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo6, isnaSp_malfo6) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable(fixed_thead = T, longtable = T) %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo7 and sp_malfo7 (missing)

```{r}
#| label: malfo7_sp_malfo7
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo7 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo7 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo7), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo7, isnaSp_malfo7) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### malfo8 and sp_malfo8 (missing)

```{r}
#| label: malfo8_sp_malfo8
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_malfo8 <- ifelse(eurocatData_merged_last_pre_DMS$sp_malfo8 == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_malfo8), "Missing", "Available")

malfoSpmalfoTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(malfo8, isnaSp_malfo8) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSpmalfoTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### syndrome and sp_syndrome (missing)

```{r}
#| label: syndrome_sp_syndrome
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_syndrome <- ifelse(eurocatData_merged_last_pre_DMS$syndrome == "-" | is.na(eurocatData_merged_last_pre_DMS$syndrome), "Missing", "Available")

malfoSyndromeTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(syndrome, isnaSp_syndrome) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

malfoSyndromeTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### Missing syndrome and malfo1

**Not admissible values**: Missing/Missing

```{r}
#| label: missing_syndrome_malfo1
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSyndrome <- ifelse(eurocatData_merged_last_pre_DMS$syndrome == "" | is.na(eurocatData_merged_last_pre_DMS$syndrome), "Missing", "Available")

eurocatData_merged_last_pre_DMS$isnaMalfo1 <- ifelse(eurocatData_merged_last_pre_DMS$malfo1 == "" | is.na(eurocatData_merged_last_pre_DMS$malfo1), "Missing", "Available")

isnaMalfo1IsnaSyndromeTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(isnaSyndrome, isnaMalfo1) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

isnaMalfo1IsnaSyndromeTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### faanom and sp_faanom

**faanom**: 1 = Same 2 = Other 3 = Same and other 4 = No 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: faanom_sp_faanom
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_faanom <- ifelse(eurocatData_merged_last_pre_DMS$sp_faanom == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_faanom), "Missing", "Available")

faanomSp_faanomTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(faanom, isnaSp_faanom) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

faanomSp_faanomTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### moanom and sp_moanom

**moanom**: 1 = Same 2 = Other 3 = Same and other 4 = No 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: moanom_sp_moanom
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_moanom <- ifelse(eurocatData_merged_last_pre_DMS$sp_moanom == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_moanom), "Missing", "Available")

moanomSp_moanomTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(moanom, isnaSp_moanom) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

moanomSp_moanomTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### sibanom and sp_sibanom

**sibanom**: 1 = Same 2 = Other 3 = Same and other 4 = No 9 = Not known

**Not admissible values**: to be defined

```{r}
#| label: sibanom_sp_sibanom
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaSp_sibanom <- ifelse(eurocatData_merged_last_pre_DMS$sp_sibanom == "-" | is.na(eurocatData_merged_last_pre_DMS$sp_sibanom), "Missing", "Available")

sibanomSp_sibanomTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(sibanom, isnaSp_sibanom) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

sibanomSp_sibanomTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### firsttri by DRUGS1

**firsttri**: 1 = Yes, medication taken in first trimester 2 = No medication taken in first trimester 4 = Medication taken, but timing unknown 9 = Not Known

**Not admissible values**: to be defined

```{r}
#| label: firsttri_drugs1
#| echo: false
#| warning: false
#| results: asis

eurocatData_merged_last_pre_DMS$isnaDrugs1 <- ifelse(eurocatData_merged_last_pre_DMS$drugs1 == "-" | is.na(eurocatData_merged_last_pre_DMS$drugs1), "Missing", "Available")

firsttriDrugs1Table <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(firsttri, isnaDrugs1) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

firsttriDrugs1Table %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

### code_pres by data_source

**code_pres**: list of codes

**data_source**: EDC SDO

**Not admissible values**: to be defined

```{r}
#| label: cod_pres_data_source
#| echo: false
#| warning: false
#| results: asis

codpresDatasourceTable <- eurocatData_merged_last_pre_DMS %>% 
  tabyl(cod_pres, data_source) %>% 
  adorn_totals( where = c("row", "col") ) %>%
  adorn_percentages("row") %>%
  adorn_pct_formatting() %>%
  adorn_ns( position = "front" ) %>%
  adorn_title("combined")

codpresDatasourceTable %>%
  kable() %>% row_spec(row = 0, background = 'lightgray') %>% column_spec(1, bold = TRUE) %>% kable_styling(latex_options = c("repeat_header", "striped"), font_size = 10) %>%
  print()

cat("\n\\newpage\n")
```

## System info

```{r}
#| echo: false
#| warning: false

Sys.time()
sessionInfo()
```
